%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%

% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins

% title on top of the document
\maintitle{Tzu-Chiao Yeh}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:su3g4284zo6y7@gmail.com}{su3g4284zo6y7\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}886-930825802\sbull
\href{https://tz70s.github.io}{tz70s.github.io}\sbull
\href{https://github.com/tz70s}{github.com/tz70s}\sbull
Taipei\sbull
Taiwan
%\\
%Taipei\sbull
%Taiwan
\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

% \roottitle{Summary}  % a root section title

% \vspace{-1.3em}  % some vertical spacing
% \begin{multicols}{2}  % open a multicolumn environment
% \noindent
% \textbf{Software Engineer} particularly interested in distributed system, programming language (FP), and software infrastructure.
% Prolific open-sourcer with over 100 Github repos and patches accepted into over 20 projects.
% Passionate learner and researcher for cutting-edge technologies and solving hard problems.
% \end{multicols}

% \spacedhrule{0em}{-0.4em}

\roottitle{Experience}

\vspace{0.2em}

\headedsection  % sets the header for the section and includes any subsections
  {University of Washington}
  {\textsc{Seattle, WA, USA}} {
  \vspace{0.2em}
  \headedsubsection
    {Visiting Student in IPL Lab (ECE)}
    {May \apo1 -- July \apo25}
    {\bodytext{
      \vspace{0.2em}
      Research on programming language and distributed system 
      issues in machine learning/deep learning area.
    }}
}

\vspace{0.2em}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://summerofcode.withgoogle.com/archive/2018/projects/5211013825691648/}{Apache Software Foundation}}
  {\textsc{Remote}} {%
  \vspace{0.2em}
  \headedsubsection
    {Google Summer of Code Intern}
    {May \apo18 -- Aug \apo18}
    {\bodytext{
    \vspace{0.2em}
    Working on Apache OpenWhisk by joining the design and implementing a new scheduler to avoid hot-path bottleneck and better resource usage with 3x performance gained.
    The technical stack was based on Scala, Akka, Kafka, CouchDB, Ansible, Docker and Kubernetes, etc.}}
}

\vspace{0.7em}

\spacedhrule{0em}{-0.4em}

\roottitle{Education}

\vspace{0.2em}

\headedsection
  {\href{https://www.ntu.edu.tw}{National Taiwan University}}
  {\textsc{Taipei, Taiwan}} {%
  \headedsubsection
    {Master degree in Electrical Engineering, Computer Science Program}
    {2016 -- 2019}
    {\bodytext{
      \vspace{0.2em}
      Research on distributed programming model and framework design for edge/cloud computing and IoT.}}
    \headedsubsection
    {Thesis: A Framework for Building Reactive Applications in Edge Computing}{}{}
}

\vspace{0.2em}

\headedsection
  {\href{https://web.ncku.edu.tw}{National Cheng Kung University}}
  {\textsc{Tainan, Taiwan}} {%
  \headedsubsection
    {Bachelor degree in Computer Science and Information Engineering}
    {2011 -- 2016 (dropout)}
    {\bodytext{
      \vspace{0.2em}
      Earned a honorable mention of senior independent study, an interactive data visualization system based on Bootstrap, Jquery, D3.js and Flask for Spotify artists recommendation.
    }}
}

\vspace{0.7em}

\spacedhrule{0em}{-0.4em}

\roottitle{Skills}

\vspace{0.2em}

\inlineheadsection
  {Programming Languages:}
  {Proficient in Scala, Haskell, Java, Go, Rust and many other prior-experienced.}

\vspace{0.2em}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Specialties:}
  {Distributed System, Functional Programming, Web Backend, Software Infrastructure.}

\vspace{0.2em}
\inlineheadsection
  {Tools \& Frameworks:}
  {Akka Toolkit, Play Framework, Cats, Cats-Effect, Fs2, gRPC, ScalaTest, Junit, Jmh, MySQL, Redis, Etcd, Kafka, Spark, OpenWhisk, Kubernetes, Docker, Travis CI, Git, GCP.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Selected Projects}

\vspace{0.2em}

\inlineheadsection
  {\href{https://github.com/tz70s/reactive-tomato}{Reactive Tomato}:}
  {Distributed reactive programming framework in Haskell designed for decentralized and unreliable environment.
  The reactive abstractions are based on Pipes monad transformer and Redis for intra-cluster event propagation. }

\vspace{0.2em}

\inlineheadsection
  {\href{https://github.com/tz70s/gpuflow}{GPUFlow}:}
  {GPU accelerated network packet processing (L3 routing in LPM trie search) based on Intel DPDK and Nvidia CUDA for 
  kernel bypassing networking and GPU memory latency hiding.}

\vspace{0.2em}

\inlineheadsection
  {\href{https://github.com/tz70s/pars}{Pars}:}
  {Distributed framework for Fs2 based monadic stream processing with configurable replication based on decentralized deployment model and custom coordinator and scheduler.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{OSS Experience}

\vspace{0.2em}

\inlineheadsection
  {\href{https://github.com/apache/incubator-openwhisk/commits/master?author=tz70s}{Apache OpenWhisk}:}
  {Contributing to experimental scheduler performance improvement and minor fixes on distributed tracing, 
  refactoring and build system, etc.}

\vspace{0.2em}

\inlineheadsection
  {Akka Toolkit:}
  {Contributing to \href{https://github.com/akka/akka/commits/master?author=tz70s}{Akka} and \href{https://github.com/akka/akka-grpc/commits/master?author=tz70s}{Akka gRPC}.}

\vspace{0.2em}

\inlineheadsection
  {Over 100+ repos and OSS contributions (20+ projects) can be found on my \href{https://github.com/tz70s}{Github page}.}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Publication}

\vspace{0.2em}

\inlineheadsection
  {Tzu-Chiao Yeh,}
  {Yung-Li Hu, Yennun Huang, Sy-Yen Kuo, \emph{"
  Fog Emulator: An Emulator Toolkit for Application Development on Fog Computing based on Containerization Technology,"} Taiwan Conference on Software Engineering, 2018}

\vspace{0.2em}

\spacedhrule{1.6em}{-0.4em}

% \roottitle{Talks}

% \vspace{0.2em}

% \inlineheadsection
%   {A Serverless Framework for Event-driven Application Development on Edge Computing}
%   {in 28th CJK Workshop, KAIST, Korea, May 24-26, 2018.}

% \vspace{0.2em}

% \inlineheadsection
%   {A Design of Container-based Emulator for Fog Computing}
%   {in 26th CJK Workshop, NTUST, Taiwan, May 22-24, 2017.}

\end{document}
